---
title: "Code Convertion"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Code Convertion}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| include = FALSE
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
#| label = "setup"
library(rpkgkit)
```

# Qualify package function calls

`make_func_call_explicit()` adds namespace qualifiers to calls from selected
packages. `package_func_call_explicit()` applies the same operation throughout
a package.

```{r}
#| label = "make_func_call_explicit"
file <- tempfile(fileext = ".R")
writeLines(
  c(
    "starwars |>",
    "  mutate(name, bmi = mass / ((height / 100)^2)) |>",
    "  select(name:mass, bmi)"
  ),
  file
)

make_func_call_explicit(file, use_packages = "dplyr")
readLines(file) |> cli::cli_code()
```

# Find unmatched glue braces

`detect_lost_glue_brace()` checks one file; `package_lost_glue_brace()` checks
an entire package. Both support `glue` and `cli` expressions.

```{r}
#| label = "detect_lost_glue_brace"
file <- tempfile(fileext = ".R")
writeLines(
  c(
    'name <- "world"',
    'msg <- glue::glue("Hello, {name!")',
    'cli::cli_alert_warning("{.field warning}}")'
  ),
  file
)

detect_lost_glue_brace(file)
```

# Name positional arguments

`make_func_arg_explicit()` makes arguments in one file explicit, and
`package_func_arg_explicit()` applies this transformation across a package.

```{r}
#| label = "make_func_arg_explicit"
file <- tempfile(fileext = ".R")
writeLines("vapply(1:9, function(x) x * 2, numeric(1))", file)
make_func_arg_explicit(file)
readLines(file) |> cli::cli_code()
```

# Rename functions

Use `rename_func()` to apply a naming style to function definitions in a file.

```{r}
#| label = "rename_func"
file <- tempfile(fileext = ".R")
writeLines("this_is_a_function <- function() message('Hello, world')", file)
rename_func(file, style = "camelCase")
readLines(file) |> cli::cli_code()
```

# Detect print() and cat()

`detect_print_and_cat()` reports `print()` and `cat()` calls in one file.
`package_print_and_cat()` checks an entire package. Set `fix = TRUE` to replace
those calls in the selected file with `message()`.

```{r}
#| label = "detect_print_and_cat"
file <- tempfile(fileext = ".R")
writeLines("print('Hello, world')", file)
detect_print_and_cat(file)
```

```{r}
#| label = "detect_print_and_cat_fix"
detect_print_and_cat(file, fix = TRUE)
readLines(file) |> cli::cli_code()
```

# Convert function syntax

Convert between `function()` and the short `\()` syntax.

```{r}
#| label = "convert_func_syntax"
file <- tempfile(fileext = ".R")
writeLines("f <- function(x) x^2", file)
convert_func_syntax(file, "to_lambda")
readLines(file) |> cli::cli_code()
```

```{r}
#| label = "convert_func_syntax_to_explicit"
convert_func_syntax(file, "to_explicit")
readLines(file) |> cli::cli_code()
```

# Modernize knitr chunk headers

`convert_knitr_chunk_header()` converts legacy R Markdown chunk options to the
current comment-based syntax.

```{r}
#| label = "convert_knitr_chunk_header"
file <- tempfile(fileext = ".Rmd")
writeLines(c("```{r, echo=TRUE, fig.width=10}", "x <- 1", "```"), file)
convert_knitr_chunk_header(file)
readLines(file) |> cli::cli_code()
```

# Add integer suffixes

`convert_int_literals()` adds `L` to bare integer literals while leaving
strings, comments, floating-point values, and existing suffixes unchanged.

```{r}
#| label = "convert_int_literals"
file <- tempfile(fileext = ".R")
writeLines("x <- seq_len(10) # length 10", file)
convert_int_literals(file)
readLines(file) |> cli::cli_code()
```

Use `package_convert_int_literals()` to process `.R` and `.r` files below a
package's `R/` and `tests/` directories.

```r
package_convert_int_literals(".")
```

# Convert non-ASCII source code

`convert_nonascii_code()` converts non-ASCII source to Unicode escape sequences
when needed for CRAN-compatible source files. It accepts either a file path or
an R expression.

```{r}
#| label = "convert_nonascii_code"
file <- tempfile()
writeLines("foo <- \\() message('滚滚长江东逝水')", file)
convert_nonascii_code(file, overwrite = TRUE)
readLines(file) |> cli::cli_code()
```

```{r}
#| label = "convert_nonascii_code_expr"
convert_nonascii_code({
  cli::cli_alert_info("明月几时有")
  cli::cli_alert_warning("把酒问青天")
})
```
