---
title: "Edit NEWS"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Edit NEWS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| include = FALSE
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



# Maintain NEWS.md

Here we create a template for editing NEWS.md

```{r}
#| label = "setup",
#| echo = FALSE
library(rpkgkit)
tmpdir <- tempdir()
usethis::create_package(tmpdir, open = FALSE)
writeLines(
  c("# pkgname v0.0.0.9000", "", "* This is a template for editing NEWS.md"),
  file.path(tmpdir, "NEWS.md")
)
```

```{r}
#| label = "show_raw"
news_md_show(path = tmpdir)
```

Add a new entry using the package version in `DESCRIPTION`:

```{r}
#| label = "add-entry"
news_md_add_entry(
  entry = "Add foo function",
  category = "NEW FEATURES",
  path = tmpdir
)
```

```{r}
#| label = "show_updated"
news_md_show(path = tmpdir)
```

Specify a different category when needed:

```{r}
#| label = "add-entry-with-version"
news_md_add_entry(
  entry = "Fixed bugs in `foo()`",
  category = "BUG FIXES",
  contributor = "Jack",
  path = tmpdir
)
```

```{r}
#| label = "show_updated2"
news_md_show(path = tmpdir)
```

As you can see, different categories belong to the same version are grouped together.

Validate the resulting file against the package's NEWS formatting rules:

```{r}
#| label = "news_check"
news_md_check(path = tmpdir)
```

`"File should end with a blank line"` just follows the same rule as `DESCRIPTION`. But generally, there are very few items that need to be checked for NEWS.md compared with other files in an R package, and these requirements are not mandatory; however, they can indeed standardize NEWS writing.