---
title: "Package Setup & Maintenace"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Package Setup & Maintenace}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| include = FALSE
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
#| label = "setup",
#| echo = FALSE
library(rpkgkit)
dir <- tempdir()
usethis::create_package(path = dir, open = FALSE)
```

# Create package infrastructure

## A spinner startup message

`use_zzz()` creates a package documentation file with `.onLoad`, `.onAttach`,
and `%||%`. It is similar to `usethis::use_package_doc()` while also providing
a useful starting template.

```{r}
#| label = "use_zzz"
use_zzz(path = dir, open = FALSE)
```

## Check missing function in `_pkgdown` reference

`check_pkgdown_reference()` identifies exported functions that are absent from
the `reference` section of `_pkgdown.yml`.

```{r}
#| label = "check_pkgdown_reference",
#| eval = FALSE
check_pkgdown_reference(pkg = dir)
```

# Vendor permissively licensed code

`use_vendor()` records attribution and licensing information when incorporating
selected source files from a permissively licensed GitHub R package. It creates
an `inst/vendor/` directory, a `R/vendor-*.R` file, and updates relevant
`DESCRIPTION` fields.

```{r}
#| label = "use_vendor"
use_vendor(
  pkg = "WangLabCSU/rpkgkit",
  "43_use_vendor.R",
  branch = "main",
  path = dir
)
```

Only packages with a supported permissive license can be vendored. Review the
acknowledgement text printed by the function and add it to your README when
appropriate.

```{r}
rpkgkit::PERMISSIVE_LICENSE
```

# `usethis` extensions

Use the following helpers from the package root:

## Use R 4.1.0 version

R 4.1.0 introduced the pipe (`|>`) and anonymous function `\()`. If these syntaxes need to be used in a package, the R package must require at least R version 4.1.0.

```{r}
#| label = "use_r_v4.1.0"
use_r_v4.1.0(path = dir)
```

## Add URL in `DESCRIPTION`

```{r}
#| label = "use_url",
#| eval = FALSE
use_url(dir)
```

## Add bug reports URL in `DESCRIPTION`

```{r}
#| label = "use_bugreports",
#| eval = FALSE
use_bugreports(dir)
```

# Open CFF

CITATION.cff files are plain text files with human- and machine-readable citation information for software and datasets.

Code developers can include such files in their source code repositories to let others know how to correctly cite their software.

```{r}
#| label = "use_cff",
#| eval = FALSE
open_cffinit()
```

**This cannot replace `usethis::use_citation()`**, it just complements project.


# Global ignore-file templates

Use `add_global_rbuildignore()` and `add_global_gitgnore()` to add the
corresponding global ignore-file templates to a package.

```{r}
#| label = "add_global_rbuildignore"
add_global_rbuildignore(path = dir)
```

```{r}
#| label = "add_global_gitgnore"
add_global_gitgnore(pkg = dir)
```
