---
title: "rpkgkit standalone scripts"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rpkgkit standalone scripts}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| include = FALSE
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
#| label = "setup",
#| eval = FALSE
library(rpkgkit)
dir <- file.path(tempdir(), "example")
usethis::create_package(dir, open = FALSE)
usethis::local_project(dir)
usethis::use_readme_md(open = FALSE)
```

```{r}
#| label = "setup_bg",
#| include = FALSE,
#| echo = FALSE,
#| message = FALSE
library(rpkgkit)
```

# Import standalone helpers

`rpkgkit` includes utilities that can also be imported directly into another
project with `usethis::use_standalone()`.

```r
usethis::use_standalone("WangLabCSU/rpkgkit", "args_to_func")
```

## Match arguments to functions

The `args_to_func.R` standalone script provides helpers for matching a list of
arguments to compatible functions.

```r
f1 <- function(a, b) a + b
f2 <- function(x, y, ...) x * y
f3 <- function(p, q) p - q

args <- list(a = 1, b = 2)
match_func_to_args(args, f1, f2, f3)
```

```r
args <- list(a = 1, b = 2, x = 3, y = 4)
foo <- function(x, y = 1) x + y
filter_args_for_func(args, foo)
```

## Show the caller of a cli message

The `caller_cli.R` standalone script decorates a `cli` function so its output
identifies the caller.

```r
decorated <- add_caller_to_cli(cli::cli_alert_info)
foo1 <- \() {
  decorated("<- where is this called from?")
}
foo2 <- \() foo1()
bar <- function() foo2()
bar()
```

## Use colored cli output

The `colorful_cli.R` standalone script creates a `cli` environment with
convenient color classes.

```r
color_cli <- create_colorful_cli_env()
color_cli$cli_alert_danger("{.red This is a red message}")
color_cli$cli_alert_info("{.blue This is a blue message}")
color_cli$cli_alert_info("{.orange This is an orange message}")

color_cli2 <- create_colorful_cli_env(cli_theme = generate_color_theme())
color_cli2$cli_alert_success(
  "{.violetred3 R}{.orange a}{.yellow i}{.green n}{.cyan b}{.blue o}{.purple w}"
)
```

## Add timestamps to cli output

The `ts_cli.R` standalone script creates timestamped `cli` functions.

```r
ts_cli <- create_ts_cli_env()
ts_cli$cli_alert_info("Hello, world!")
```

# Manage standalone files in a package

Use `inquire_standalone()` to inspect standalone files in a GitHub repository
and `browse_standalone()` to search supported repositories.

```{r}
#| label = "inquire"
try(inquire_standalone("r-lib/rlang"))
```

```{r}
#| label = "browse"
try(browse_standalone())
```

Create a local standalone file with a standard metadata header:

```{r}
#| label = "create",
#| eval = FALSE
create_standalone("foo", open = FALSE)
```

After editing standalone files, refresh their `last-updated` field:

```{r}
#| label = "update timestamp",
#| eval = FALSE
update_time_in_standalone(path = "./R/standalone-foo.R")
```

Add a dated changelog entry to one or more standalone files:

```{r}
#| label = "add changelog",
#| eval = FALSE
add_changelog_in_standalone("R/standalone-foo.R", "Added foo function")
```
